TacticToe: Learning to Prove with Tactics

### 2018-03-21 tactictoe_jv.tex
Fix Cezary's todos

We estimate the similarity between two objects $o_1$ and $o_2$
through their respective feature sets $f_1$ and $f_2$.
The estimation is based on the frequency of the features in the intersection of
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features
are, the more similar two goals should be. The relative rarity of each feature
can be estimated by calculating its TF-IDF weight~\cite{Jones72astatistical}.
We additionally raise these weights to the sixth power giving
even more importance
to rare features. The second and third authors found this modification 
experimentally 
optimal~\cite{ckju-pxtp13}. \todoi {Cezary: Josef says sixth 
power is not 
in this 
citation}.

@@

%A recent improvement on this system~\cite{}\todo{Cezary: could not remember
%the
%reference that you gave me here i think it was CICM 2017} includes the
%possibility to
%substitute theorems appearing in tactics by ones belonging to the same
%cluster.
%In this work, we are also able to predict theorems appearing as arguments of
%tactics but we rely only on information from the current goal. Combining the
%two approaches by predicting from the goal and from the original tactic
%arguments is more difficult but is likely to produce more suitable lemmas.
%
Proof patching: \cite{RingerYLG18}
\todoi{Cezary; comment on proof patching or remove the citation.}

\todoi{Cezary; add ltac and eisbach or remove PSL if you think it is not worth 
mentionning.}
A similar effort for stronger automation is performed in \isabelle. Nagashima
developed a proof strategy language PSL~\cite{NagashimaK17psl} which allows the
user to
program with regular tactics and combine them with tools such as
\sledgehammer.
Selection of tactics from data collected in recorded proofs is in development
but for now it is up to the user to come up with a good meta-tactic.

>>>>

We estimate the similarity between two objects $o_1$ and $o_2$
through their respective feature sets $f_1$ and $f_2$.
The estimation is based on the frequency of the features in the intersection of
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features
are, the more similar two goals should be. The relative rarity of each feature
can be estimated by calculating its TF-IDF weight~\cite{Jones72astatistical}.
We additionally raise these weights to the sixth power giving
even more importance
to rare features~\cite{BlanchetteGKKU16}.

@@

%A recent improvement on this system~\cite{}\todo{Cezary: could not remember
%the
%reference that you gave me here i think it was CICM 2017} includes the
%possibility to
%substitute theorems appearing in tactics by ones belonging to the same
%cluster.
%In this work, we are also able to predict theorems appearing as arguments of
%tactics but we rely only on information from the current goal. Combining the
%two approaches by predicting from the goal and from the original tactic
%arguments is more difficult but is likely to produce more suitable lemmas.
%
Proof Patching \cite{RingerYLG18} is an approach that attempts to learn the
proof changes necessary for a modification of a prover library or system. The
approach is hard to apply for new proofs. On the other had, \tactictoe could also
try to learn from different versions of the prover library.

% \todoi{Cezary; add ltac and eisbach or remove PSL if you think it is not worth 
% mentionning.}
% A similar effort for stronger automation is performed in \isabelle. Nagashima
% developed a proof strategy language PSL~\cite{NagashimaK17psl} which allows the
% user to
% program with regular tactics and combine them with tools such as
% \sledgehammer.
% Selection of tactics from data collected in recorded proofs is in development
% but for now it is up to the user to come up with a good meta-tactic.
